---
title: "Coding Assignment 03"
date: "`r Sys.Date()`"
output: html_document
text.align: justify
---

----

### Type your student name and ID

Name and ID: Jayti Saparia and 702792621 

---

#### Task 1: Download the Admission dataset and set the work directory:

```{r}
# Make sure to set the work directory where you saved the dataset
#done
```

----

#### Task 2: Download and load the required packages:

```{r}
# your code goes here
#loading required libraries
library(ggplot2)
library(pastecs)
library(psych)
library(readr)
library(naniar)
library(mice)
```

----

#### Task 3: Load, view and return the structure of the dataset.

```{r}
# your code goes here
Admission <- read.csv("Admission.csv") #assigning dataset to a variable
#View(Admission) #viewing dataset
str(Admission) #returing the str of the dataset
```

----

#### Task 4: Stroing categorical variables as factors in the dataset

```{r}
# your code goes here
#storing categorical variable as factor of following varibales
Admission$Major <- as.factor(Admission$Major)
Admission$School_GPA <- as.factor(Admission$School_GPA)
Admission$Admitted <- as.factor(Admission$Admitted)
```

----

#### Task 5: Return Summary Statistics of the Admission Dataset:

```{r}
# your code goes here
summary(Admission) #returning the summary
```

----

#### Task 6: Summary statistics using the pastecs package.

```{r}
# your code goes here
#returning the summary using pastecs package
options(scipen = 999)
stat.desc(Admission)
```

----

#### Task 7: Using the describe function of the psych package to get the Summary statistics for all variables.

```{r}
# your code goes here
describe(Admission) #returning the summary of the dataset
```

----

#### Task 8: Using the describeBy function to get the Summary statistics for all variables by Major.

```{r}
# your code goes here
describeBy(Admission ~ Major) # summary categorized based on the Major variable
```

----

#### Task 9: Using the describeBy function to get the Summary statistics for all variables by Admitted

```{r}
# your code goes here
describeBy(Admission ~ Admitted) #summary statistics for all variables by Admitted
```


#### Task 10: Download the Students dataset and set the work directory:

```{r}
# Make sure to set the work directory where you saved the Students dataset
#done
```

----

#### Task 11: Load, view and return the structure of the Students dataset.

```{r}
# your code goes here
Students <- read.csv("Students.csv") #assigning a varible to the data set file
#View(Students) #viewing dataset
str(Students) #returning the str of the dataset
```

----

#### Task 12: Exploring the dataset for missing values using the naniar package.

```{r}
# your code goes here
#calculating missing values and other things of Student dataset
n_miss(Students)
n_complete(Students)
pct_complete(Students)
pct_miss(Students)
pct_miss_case(Students)
pct_complete_case(Students)
gg_miss_var(Students, show_pct = TRUE) #creating a graph of missing values
vis_miss(Students) #creating a heatmap of missing values 

```

----

#### Task 13: Data Imputation.

```{r}
# your code goes here
imputed_dataset = mice(Students, m=5, method = c("", "pmm", "pmm", "rf", "rf", "rf"), maxit=5) #data imputation
```

----

#### Task 14: Viewing the clean Imputed Dataset.

```{r}
# your code goes here
imputed_dataset$imp$GRE_Score #retrieving mean od GRE scrore in imputed dataset 
final_imputed_ds = complete(imputed_dataset, 1) # choosing 1st dataset as I think it's closet one
#View(final_imputed_ds) #viewing imputed ds
```
