---
title: "Coding Assignment 02"
date: "`r Sys.Date()`"
output: html_document
text.align: justify
---

----

### Type your student name and ID

Name and ID: Jayti Saparia and 702792621

---

----

#### Task 1: Download and load the required packages:

```{r}
# your code goes here
library(ggplot2) #loading ggplot2 library
library(readr) #loading readr library
```

----

#### Task 2: Load, view and return the structure of the mtcars built-in dataset.

```{r}
# your code goes here
#loading and viewing dataset
data(mtcars)
#View(mtcars)
str(mtcars) #getting structure of mtcars
```

----

#### Task 3: Follow the instruction sheet to add box plot.

```{r}
# your code goes here
ggplot(data= mtcars, mapping = aes(x=factor(cyl), y=mpg)) + #assigning values for a graph
  geom_boxplot(width=0.3) + #drawing boxplot
  labs(x="Cyl", y="mpg", title="Box Plots") + #adding labels
  stat_summary(fun="mean", geom="point", size=1.5, shape=21, color="blue") #adding mean to the graph
  
```

----

#### Task 4: Saving the plot as "Box Plot.png".

```{r}
# your code goes here
ggsave("Box Plot.png") #saving the graph
```

----

#### Task 5: Follow the instruction sheet to add a facetted histogram.

```{r}
# your code goes here
ggplot(data=mtcars,aes(x= mpg)) + #adding x axis value
  geom_histogram(binwidth = 5, color="white", fill="blue4") + #calling function to draw histogram
  facet_wrap(~ gear, nrow=3) + #splitting graph
theme_bw() #adding theme + 
ggsave("MPG facetted by Gear.png") #saving the image
```

----

#### Task 6: Follow the instructions sheet to add a histogram .

```{r}
# your code goes here
ggplot(data=mtcars,aes(x= mpg)) + #adding x axis value
  geom_histogram(bins = 4, color="white", fill="red") + #calling function to draw histogram
  labs(x="Mile per Gallon (mpg)", y="counts", title="A Histogram for MPG", subtitle="mtcars dataset") + #adding labels
theme_bw() #adding theme 

```

----

#### Task 7: Follow the instructions sheet to add a facetted histogram.

```{r}
# your code goes here
ggplot(data=mtcars, aes(x=carb, fill=factor(cyl))) + #assigning values for x axis
  geom_histogram(binwidth=3, color="blue") + # for histogram 
  labs(x="Carburetors", y="Frequency")+ #adding labels
theme_light() + #adding theme
  facet_wrap(~ cyl) + #adding facet 
  theme(legend.position="top")  #adjusting legend position
ggsave("Facetted histogram.png")
```

----

#### Task 8: Follow the instructions sheet to add a bar plot.

```{r}
# Your code goes here
ggplot(data=mtcars, aes(x=factor(cyl), fill=factor(cyl))) + #assigning x axis 
  geom_bar(width=0.5) + #creating bar graph
  theme_bw() + #adding a theme
  labs(x="Cylinder", y="Count", title="Bar plot for mtcars cylinders") + #adding labels
  theme(legend.position = "none") # removing legend
ggsave("mtcars cylinders.png") #saving graph
```

----

#### Task 9: Download the Train_crash dataset and set the workdirectory where you saved the dataset.

```{r}
# Download the Train_crash dataset.
# Set the working directory where you saved the Train_crash dataset.
```

----

#### Task 10: Load, view and return the structure of the Train_ds dataset.

```{r}
# your code goes here
Train_ds <- read.csv("Train_crash.csv") #assigning new variable for csv
#View(Train_ds) #viewing dataset
str(Train_ds) #vieiwng the structure of the dataset
```

----

#### Task 11: Add a bar plot showing the Survival Rate.

```{r}
# your code goes here
ggplot(data=Train_ds, aes(x=factor(Survived), fill=factor(Survived))) + #assigning values of axis and fill
  geom_bar(width=0.5) + #for getting bar chart
  labs(x="Survived", y="Passenger Count", title="Train Crash Survival Rate") + #adding labels
  theme_light() #adding a theme

```

----

#### Task 12: Add a bar plot showing the Survival Rate by gender.

```{r}
# your code goes here
ggplot(data=Train_ds, aes(x=factor(Survived), fill=factor(Gender))) + #assigning x axis 
  geom_bar( width= 0.5) + #adding geom_bar function
  labs(x="Survived", y="Passenger Count", title = "Train Crash Survival Rate by Gender") +
  theme_bw() #adding a theme
```

----

#### Task 13: Add a bar plot showing the Ticket Class by Gender

```{r}
# your code goes here
ggplot(data=Train_ds, aes(x=factor(Tick_Class), fill=factor(Gender))) + #assigning x axis 
  geom_bar( width= 0.8, position="dodge") + #adding geom_bar function
  labs(x="Ticket Class", y="Passenger Count", title = "Ticket Class by Gender") + #adding labels
  theme_bw() #adding a theme
```


----

#### Task 14: Add a bar plot showing the Survival Rate by Ticket Class

```{r}
# your code goes here
ggplot(data=Train_ds, aes(x=factor(Tick_Class), fill=factor(Survived))) + #assigning x axis 
  geom_bar( width= 0.7, position="dodge") + #adding geom_bar function
  labs(x="Ticket Class", y="Passenger Count", title = "Train Crash Survival Rates by Class ") + #adding labels
  theme_light() #adding a theme
```

----

#### Task 15: Add a bar plot showing the Ticket Class per the Embarked Port

```{r}
# your code goes here
ggplot(data=Train_ds, aes(x=factor(Tick_Class), fill=factor(Port_embark))) + #assigning x axis 
  geom_bar( width= 0.8, position="dodge") + #adding geom_bar function
  labs(x="Ticket Class", y="Passenger Count", title = "Ticket Class per the Embarked Port") + #adding labels
  theme_light() #adding a theme
```

----

#### Task 16: Add a bar plot showing the Embarked Port Survival Rate by Ticket Class

```{r}
# your code goes here
ggplot(data=Train_ds, aes(x=factor(Survived), fill=factor(Tick_Class))) + #assigning x axis 
  geom_bar( width= 0.8, position="dodge") + #adding geom_bar function
  labs(x="Survived", y="Passenger Count", title = "Embarked Port Survival Rate by Ticket Class") +
  theme_light() + #adding a theme
  facet_wrap( ~ Port_embark) #adding facet
```

----

#### Task 17: Add a bar plot showing the Gender Survival Rate by Ticket Class

```{r}
# your code goes here
ggplot(data=Train_ds, aes(x=factor(Survived), fill=factor(Tick_Class))) + #assigning x axis 
  geom_bar( width= 0.7, position="dodge") + #adding geom_bar function
  labs(x="Survived", y="Passenger Count", title = "Gender Survival Rate by Ticket Class") +
  theme_light() + #adding a theme
  facet_wrap( ~ Gender) #adding facet
ggsave("Gender Survival Rate by Ticket Class.png") #saving the image
```

----
