---
title: "Coding Assignment 01"
date: "`r Sys.Date()`"
output: html_document
text.align: justify
---

----

---

#### Task 1: Calculate the following quantities:

1. The sum of 10.01, 25.003, and 37.5
2. The square root of 214
3. Calculate the 10-based logarithm of 90, and multiply the result with pi 
(Hint: use `log()` and `pi`).

```{r}
# your code goes here
10.01+25.003+37.5 # printing the sum 
sqrt(214) #calculating the square root
z = log(90, base = 10) #calculate log
y = pi
print(z*y) # printing the value of log*pi
```

----


#### Task 2: Assigns numbers 25 and 55 to objects x and y, like this: x<-25, y<-55

1. Calculate the product of x and y
2. Store the result in a new object called z
3. Make a vector of the objects x, y, and z. Use this command myvec<-c(x,y,z) then print it

```{r}
# your code goes here
x <-25 #assigning the value of x
y <-55 #assigning the value of y
z = x*y #priniting the product of x and y
myvec <-c(x,y,z) #creating avector of myvec
myvec #printing vector myvec
```

----

#### Task 3: The following is Jacket sales data as per the temperature: Temp(43, 39, 62), Jacket_Sold(23, 36, 13).

1. Enter the data in a data frame with two columns.
2. Print the data frame structure, no. of columns, and no. of rows
3. Print the entire data frame.
4. Print only the Jacket_Sold
5. Print the temperature when you sold 36 jackets

```{r}
# your code goes here
sales_data <- data.frame(Temp=c(43,39,62), Jacket_sold=c(23,36,13)) #creating a data frame
str(sales_data) #str of data frame
ncol(sales_data) #no of column of the data frame
nrow(sales_data) #no of rows in the data frame
sales_data[c("Jacket_sold")] #displaying only Jacket_sold
sales_data[2,1] #accessing the value of temp when 36 jackets sold
```

----

#### Task 4: Download and load the ggplot2 package.

```{r}
# your code goes here
#calling required libraries
library(ggplot2)
library(readr)
```

----

#### Task 5: Follow the instruction sheet.

```{r}
# loading USArrests data
data(USArrests)
#View(USArrests) #commenting out as I'm using Mac
str(USArrests)
```

----

#### Task 6: Follow the instruction sheet.

```{r}
# your code goes here
ggplot(data = USArrests, aes(x=UrbanPop, y=Rape))+  #difinding data for a graph
  geom_point() #for making a scatter plot
```

----

#### Task 7: Follow the instruction sheet.

```{r}
# your code goes here
ggplot(data=USArrests, aes(x=UrbanPop, y=Rape)) + #adding dataset to the graph
  geom_point(shape=15, color="blue3", size=2) #defining characterstics of points
```

----

#### Task 8: Follow the instruction sheet.

```{r}
# your code goes here
ggplot(data=USArrests, aes(x=UrbanPop, y=Rape)) + #creating a graph
  geom_point(shape=3, color="blue", size=1.5) + #adding factors to scatter points
  theme_bw() #adding a theme
```

----

#### Task 9: Follow the instruction sheet.

```{r}
# your code goes here
ggplot(data=USArrests, aes(x=UrbanPop, y=Rape)) + #creating a graph
  geom_point(shape=13, color="red", size=2) + #adding characterstics
  labs(x="Urban Population", y="Rape", title="The Relationship between Urban Population and Rape", subtitle = "Year 1973") + #added lables
  theme_classic() #added theme
```

----

#### Task 10: Saving the scatter plot as "Scatter Plot.png":

```{r}
# your code goes here
ggsave("Scatter Plot.png") #saving above graph
```

----

#### Task 11: Download the names_popularity dataset and set the work directory:

```{r}
# Make sure to set the work directory where you saved the dataset and the notebook
#downloaded new dbset and set a work directory
```

----

#### Task 12: Load, view and return the structure of the dataset.

```{r}
# your code goes here
Names <- read.csv("names_popularity-1.csv") #assigning dataset to Names Variable
#View(Names) #commenting out
str(Names) #getting a str of the dataset
```

----

#### Task 13: Create a line graph as per the instructions sheet:

```{r}
# your code goes here
ggplot(data=Names, aes(x=Year, y=Number, group=Name)) +   #calling ggplot for a graph
  geom_line(aes(color=Name), linewidth=1) +   #creating line graph
  theme_light() +  #adding themese
  labs(x="Years", y="Numbers", title = "Names' Popularity") #adding labels
```

----

#### Task 14: Saving the line graph as "Names' Popularity Line graph.png":

```{r}
# your code goes here
ggsave("Names' Popularity Line graph.png") #save the image
```

----

